A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-11-02 ms.tex
refs
mass and expansion

% Notebook: Figure-hierarch-results
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/hierarch-corner.pdf}
\caption{TODO}
\label{fig:hierarch-corner}
\end{figure}

@@

We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
From the stellar population modeling described above (\sectionname~\ref{sec:popmodel}), we find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with these parameters, shifted to the median distance and extincted given the median $A_V$ value.
Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.

@@

% TODO:
% - Stellar mass estimate

@@

\software{
    \package{Astropy} \citep{astropy, astropy:2018},
    \package{dustmaps}\footnote{\url{https://github.com/gregreen/dustmaps}},
    \package{emcee} \citep{emcee},
    \package{gala} \citep{gala},
    \package{IPython} \citep{ipython},
    \package{matplotlib} \citep{mpl},
    \package{numpy} \citep{numpy},
    \package{schwimmbad} \citep{schwimmbad},
    \package{scipy} \citep{scipy}
}

>>>>

% Notebook: Figure-hierarch-results
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/hierarch-corner.pdf}
\caption{TODO}
\label{fig:hierarch-corner}
\end{figure}

@@

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.

We use the isochrone corresponding to the median posterior sample to estimate the total stellar mass of the cluster.
By assuming we are 100\% complete to stars with $(g-i) < 0.3)$, and by assuming a Kroupa initial mass function \citep{Kroupa:TODO}, we use the number of observed stars and the isochrone to compute the total mass;
We find that $M_{\rm tot, *} \approx 1200~\msun$.
The mass and age of \clustername\ are comparable to Milky Way disk open clusters, but with a much lower metallicity, and a much larger spatial extent.
For example, the Pleiades has an age $\sim 135~\textrm{Myr}$ \citep{Gossage:2018}, but a physical size $\sim 5~\textrm{pc}$.
At a distance of $29~\kpc$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 760~\textrm{pc}$.
If it formed unbound, but with a size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.

@@

@@

\software{
    \package{Astropy} \citep{astropy, astropy:2018},
    \package{dustmaps} \citep{dustmaps},
    \package{emcee} \citep{emcee, emcee:ascl},
    \package{gala} \citep{gala},
    \package{IPython} \citep{ipython},
    \package{matplotlib} \citep{mpl},
    \package{numpy} \citep{numpy},
    \package{schwimmbad} \citep{schwimmbad},
    \package{scipy} \citep{scipy}
}
